% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Stephen D. O'Connell}
\newcommand{\CVNote}{CV prepared on {\today}.}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Stephen D. O'Connell},
pdfsubject={http://www.stephenoconnell.org},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

\usepackage{multicol}
\usepackage{changepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%
\vspace*{-1.5cm}

{\Large Stephen D. O'Connell}

{\normalsize
\par
\href{mailto:soconnell@emory.edu}
{soconnell@emory.edu}
}
\\
\href{http://www.stephenoconnell.org}
{www.stephenoconnell.org}
}
\\
Last Updated: 13 April 2026

\begin{body}

\bigskip

%%%%%%%%%%%%%%
% EDUCATION %%
%%%%%%%%%%%%%%
\vspace{-1cm}
\section
{Current}
{Current}
{PDF:Employment}

\href{http://economics.emory.edu/home/index.html}
{\textbf{Emory University, Department of Economics}}

Associate Professor
\hfill
\DatestampYMD{2022}{9}{} - Present


Assistant Professor
\hfill
\DatestampYMD{2018}{9}{} - \DatestampYMD{2022}{8}{}

\vspace*{-.2cm}

\section
{Previous}
{Previous}
{PDF:Employment}

\href{https://seii.mit.edu/}
{\textbf{Massachusetts Institute of Technology, Department of Economics}}


Postdoctoral Fellow
\hfill
\DatestampYMD{2016}{7}{} - \DatestampYMD{2018}{6}{}

\vspace*{-.2cm}

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.gc.cuny.edu/economics}
{\textbf{The Graduate Center at City University of New York}}


Doctor of Philosophy (Ph.D.) in
Economics
\hfill
\DatestampYMD{2016}{6}{}


Master of Philosophy (M.Phil.) in Economics
\hfill
\DatestampYMD{2013}{09}{}

\EntryGapNoBreak
\textbf{Boston College}
\par
Bachelor of Arts (B.A.) in
Economics
\hfill
\DatestampYMD{2007}{05}{}

%%%%%%%%%%%%%%
\vspace*{-.2cm}
\section
{Affiliations}
{Affiliations}
{PDF:Affiliations}

\NoEntryGap
\href{https://bfi.uchicago.edu/}
{\textbf{Becker Friedman Institute, University of Chicago}}
\hfill
\DatestampYMD{2025}{1}{} - \DatestampYMD{2025}{5}{}

Visiting Senior Research Associate


\EntryGapNoBreak
\textbf{JPAL/IPA Displaced Livelihoods Initiative}
\hfill
\DatestampYMD{2023}{8}{} - Present

Invited Researcher


\EntryGapNoBreak
\textbf{Households in Conflict Network}
\hfill
\DatestampYMD{2020}{4}{} - Present

Affiliate



\EntryGapNoBreak

\textbf{IZA Institute of Labor Economics}
\hfill
\DatestampYMD{2015}{12}{} - \DatestampYMD{2025}{12}{} (institute closed)

Research Affiliate

\EntryGapNoBreak
\href{www.javeriana.edu.co}
{\textbf{Pontificia Universidad Javeriana, Bogot\'{a}}}
\hfill
Summer 2016

Visiting Faculty

%%%%%%%%%%%%%%%%%
% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%

\section
{Research}
{Research}
{PDF:Research}


\subsection
{Peer-reviewed publications} 
{Journals}
{PDF:Journals}
%(equal co-authorship unless non-alphabetical)

\EntryGapNoBreak
Jackson Schneider and Stephen D. O'Connell, \textbf{``Gender differences in the adequacy of poverty-targeted food assistance programs,''} \textbf{\textit{World Development}}, \DatestampYM{2025}{}.

\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/BMOR_CareerPathGenderGap.pdf}
{Ryan Brown, Hani Mansour, Stephen D. O'Connell, and James Reeves, \textbf{``Gender Differences in Political Career Progression,''} \textbf{\textit{Journal of Economic Behavior and Organization}}, \DatestampYM{2025}{}.}

\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/AOC_EfficiencyVsEffectiveness.pdf}
{Onur Altındağ, Stephen D. O'Connell, and Rim Achour, \textbf{``Geographic poverty targeting in social protection programs: Evidence from a nationwide policy experiment,''} Working paper. \DatestampYM{2025}{}.}

\EntryGapNoBreak
Chris Karpowitz, Stephen D. O'Connell, Jessica Preece, and Olga Stoddard, \textbf{``Strength in Numbers? Gender Composition, Leadership, and Women's Influence in Teams,''} \textbf{\textit{Journal of Political Economy}}, \DatestampYM{2024}{}.

\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/OM_MakingJobTrainingWork.pdf}
{Stephen D. O'Connell and Lucas F. Mation, \textbf{``Tell us what you need: Matching public job training to local skill demand with employers' input,''} \datestampYM{2023}{}. }

\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/AOC_RefugeeAidEfx_2021.pdf}
{Onur Altındağ, Stephen D. O'Connell, \textbf{``The short-lived effects of unconditional cash transfers to refugees,''} \datestampYM{2022}{}. \textbf{\textit{Journal of Development Economics.}}}
(Original full-length working paper: \href{https://www.stephenoconnell.org/files/AOC_RefugeeAidEfx.pdf}
{\textbf{``Unconditional cash-based assistance to the poor: What do at-scale programs achieve?,''} \datestampYM{2021}{}.)}


\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/McOC_LegislativeCareers.pdf}
{Josh McCrain, Stephen D. O'Connell, \textbf{``Experience, institutions, and candidate emergence: The political career returns to state legislative service,''} \datestampYM{2022}{}. \textbf{\textit{Political Science Research and Methods}}}.

\EntryGapNoBreak
\href{https://www.stephenoconnell.org/files/BMO_IndiaElectionsCareers.pdf}
{Ryan Brown, Hani Mansour, Stephen D. O'Connell, \textbf{``Does local female political representation empower women to run for higher office? Evidence from state and national legislatures in India,''} \datestampYM{2022}{}. \textbf{\textit{World Bank Economic Review}}}.


\EntryGap
\href{https://www.stephenoconnell.org/files/AOSBCJK_TargetingRefugees.pdf}
{Onur Altındağ, Stephen D. O'Connell, Aytug Sasmaz, Zeynep Balcioglu, Paola Cadoni, Matilda Jerneck, Aimee Kunze Foong, \textbf{``Targeting humanitarian aid using administrative data: model design and validation,''} \datestampYM{2021}{}. \textbf{\textit{Journal of Development Economics.}}} 

\EntryGap
Kevin Croke, Andualem Mengistu, Stephen D. O’Connell, and Kibrom Tafere, \textbf{``The Impact of Ethiopia's Health Facility Construction Campaign on Health Service Utilization and Outcomes: A Secondary Analysis of Spatially-Linked Survey and Facility Location Data,''} \datestampYM{2020}{}. \textbf{\textit{BMJ Global Health.}}

\EntryGap
\href{https://www.mitpressjournals.org/doi/pdf/10.1162/rest_a_00802}
{Stephen D. O'Connell, \textbf{``Can quotas increase the supply of candidates for higher-level positions? Evidence from local government in India,''} \textbf{\textit{Review of Economics and Statistics}}, vol.~102, no.~2, pp.~65-78, \datestampYM{2020}{}}.

\EntryGap

\href{https://doi.org/10.1016/j.jdeveco.2018.08.004}
{Stephen D. O'Connell, \textbf{``Political inclusion and educational investment: Estimates from a national policy experiment in India,''}
\textbf{\textit{Journal of Development Economics}}, vol.~135, pp.~478-487, \datestampYM{2018}{}}.


\EntryGap
\href{http://www.stephenoconnell.org/files/ACWO2016_AER_Shortages.pdf}
{Hunt Allcott, Allan Collard-Wexler, and Stephen D. O'Connell,
\textbf{``How Do Electricity Shortages Affect Industry? Evidence from India,''}
\textbf{\textit{American Economic Review}},
vol.~106,
no.~3,
pp.~587--624,
\DatestampYM{2016}{}.}


\EntryGap
\href{http://elibrary.worldbank.org/doi/abs/10.1596/1813-9450-6060}
{Klaus Desmet, Ejaz Ghani, Stephen D. O'Connell and Esteban Rossi-Hansberg,
\textbf{``The Spatial Development of India,''}
\textbf{\textit{Journal of Regional Science}},
vol.~55,
no.~1,
pp.~10--30,
\DatestampYM{2015}{}.}

\EntryGapNoBreak

\href{http://www.stephenoconnell.org/files/GKO_ReservationsEntry.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
\textbf{``Political Reservations and Women's Entrepreneurship in India,''}
\textbf{\textit{Journal of Development Economics}},
vol.~108,
pp.~138--153,
\DatestampYM{2014}{}.}


\EntryGap

\href{http://www.stephenoconnell.org/files/Ghani_Kerr_OConnell_JEG13.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
\textbf{``Local Industrial Structures and Female Entrepreneurship in India,''}
\textbf{\textit{Journal of Economic Geography}},
vol.~13,
no.~6,
pp.~929--964,
\DatestampYM{2013}{}.}

\EntryGapNoBreak

\href{http://www.stephenoconnell.org/files/Ghani_Kerr_OConnell_RS_2013.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
\textbf{``Spatial Determinants of Entrepreneurship in India,''}
\textbf{\textit{Regional Studies}},
vol.~48,
no.~6,
\DatestampYM{2013}{} (special issue).} 
 
\section
{In progress}
{In progress}
{PDF:IP}

\subsection
{Ongoing projects}
{IPs}
{PDF:IPs}

\EntryGapNoBreak
Andrea Caflisch, Daniel Masterson,  Stephen D. O'Connell, and Julia Smith-Omomo, ``From Displacement to Resilience: Economic Recovery Aid and Social Cohesion in Post-War Iraq,'' At-scale field experiment; Baseline collected June 2024. Partners: IOM Iraq. Funding: IOM Iraq; JPAL/IPA Displaced Livelihoods Initiative \$227,885.
 
\EntryGapNoBreak
Stephen D. O'Connell and Nicholas Skelley, ``Endogenous household reorganization and social welfare program manipulation,'' \datestampYM{2022}{}. 

 
 
\section
{Other Research}
{Other Research}
{PDF:Peda}

\subsection
{Peer-reviewed publications related to teaching and pedagogy in higher education}
{JournalsPed}
{PDF:JournalsPed}

\EntryGapNoBreak
David Jaeger et al. \textbf{``The Global COVID-19 Student Survey: First wave results,"} \textbf{\textit{COVID Economics}} 79, 2021.


\EntryGapNoBreak
Stephen D. O'Connell and Guido Lang, \textbf{``Can Personalized Nudges Improve Learning in Hybrid Classes? Experimental Evidence From an Introductory Undergraduate Course,"}  \textbf{\textit{Journal of Research on Technology in Education}} 50(2): 105-119, 2018.

\EntryGapNoBreak
\href{http://www.stephenoconnell.org/files/DPRTjpam_final.pdf}
{Theodore Joyce, Dahlia Remler, David Jaeger, Onur Altındağ, Stephen D. O'Connell, and Sean Crockett,
\textbf{``On Measuring and Reducing Selection Bias with a Quasi-Doubly Randomized Preference Trial,''}
\textbf{\textit{Journal of Policy Analysis and Management}},
vol.~36,
no.~2,
pp.~438--459,
\DatestampYM{2017}{}.} 

\EntryGapNoBreak
\href{http://www.djaeger.org/research/pubs/EER_forthcoming.pdf}
{Theodore J. Joyce, Sean Crockett, David A. Jaeger, Onur Altındağ and Stephen D. O'Connell,
\textbf{``Does Classroom Time Matter?''}
\textbf{\textit{Economics of Education Review}},
vol.~46
pp.~64-77,
\DatestampYM{2015}{}.} 







%%%%%%%%%%%%%%%%%%%%%%%%%%
% TEACHING & PROFESSIONAL EXPERIENCE  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Teaching}
{Teaching}
{PDF:Teaching}

\textbf{Emory University},
Atlanta, GA, USA


\par
Honors Thesis Seminar
\hfill
%F2018 (8.48/9), F2019 (8.43/9), F2020 (8.76/9), F2021 (8.45/9)

\par
Econometrics I
\hfill
%F2019 (7.98/9), S2020 (8.10/9), F2021 (8.28/9)

\par
Causal Inference/Policy Analysis
\hfill
%S2020 (8.21/9)

Undergraduate Research in Economics
\hfill
%F2020 (8.90/9)

Labor Economics (Graduate)
\hfill
%S2019 (8.70/9), S2021 (8.07/9)


\smallskip
\smallskip


\textbf{Pontificia Universidad Javeriana, Bogot\'{a}},
Bogot\'{a}, D.C., Colombia
\par
Behavioral Economics
\hfill
\DatestampYMD{2016}{06}{}

\smallskip
\smallskip

\textbf{Hunter College, City University of New York},
New York, NY, USA
\par
Econometrics I
\hfill
\DatestampYMD{2011}{08}{} --
\DatestampYMD{2014}{05}{}
\par
Economic Development
\hfill
\DatestampYMD{2012}{08}{} --
\DatestampYMD{2012}{12}{}
\par
Advisor, Senior Honors Thesis (2 students)
\hfill
\DatestampYMD{2013}{01}{} --
\DatestampYMD{2013}{05}{}


\section
{Student mentoring}
{Student mentoring}
{PDF:Mentoring}

\par
\textbf{College Research Mentorship Programs}
\hfill

\par
\textit{\textbf{SIRE}}
\par
2018 - 2019: Belicia Rodriguez

\textit{\textbf{CLSS}}
\par
2018 - 2019: Andrew Kliewer

\textit{\textbf{SURE}}
\par
Summer 2021: Nicholas Skelley
\par
Summer 2025: Lucy Liu

\bigskip

\par
\textbf{Economics Dept. Honors Program}
\hfill
Since 2018
\par
\textit{\textbf{Thesis Advisor}}
\par
2018 - 2019: Reiko Laski. Placement: Federal Reserve Bank of Richmond.
\par
\smallskip
2019 - 2020: Miaomiao Zhang. Placement: HBS Strategy Group Predoctoral Research Fellowship.
\par
\smallskip
2020 - 2021: Junaid Ahmed. Placement: Georgia Tech Masters in Computer Science.
\par
\smallskip
2021 - 2022: Raoul Dubey. Placement: NERA Economic Consulting.
\smallskip
2022 - 2023: Jackson Schneider. Placement: LSE MSc in Development Studies.
\smallskip
\par
2024 - 2025: Tianqi Zhang
\par
\smallskip
2024 - 2025: Ettan Patel
\smallskip
\par
2025 - 2026: Lucy Liu
\smallskip
\par
\textit{\textbf{Committee member}}
\par
2018 - 2019: Lucy Hansen, Claudia Hurowitz
\par
2019 - 2020: Andrew Kliewer (Pol. Sci.), Raya Machaca
\par
2020 - 2021: Jasmine Cui, Benjamin Weiner
\par
2021 - 2022: Angela Choksi, Nicholas Skelley
\par
2022 - 2023: Matthew Angelo Fernandez Joesoep, Steven Luo, Jackson Pentz 
\par
2023 - 2024: Harper Wang, Elaine Han
\par
2024 - 2025: David Lee (Pol. Sci.)
\par
2025 - 2026: Jacky An (DDS)
\bigskip

\par
\textbf{Economics Dept.  Ph.D. Program}
\par
\textit{\textbf{Dissertation Committee Member}}
\par
Kaylyn Sanbower, ``Essays on the Effects of Information Disclosure in Hospital Markets'' (2022)
\par
\smallskip
Sam Wunderly, ``Studies of the Relationships Between Labor Unions, the Labor Environment, and Health'' (2022)
\par
\smallskip
Katie Leinenbach, ``Essays on Marijuana Use in Older Adults'' (2025)

\section
{College/
Department Service}
{Service}
{PDF:Service}
\par
\textbf{Economics Dept. Honors Program}
\par
Coordinator
\hfill
\DatestampYMD{2018}{08}{} - Present

\smallskip

\par
\textbf{Economics Dept., Undergraduate Research}
\par
Director
\hfill
\DatestampYMD{2020}{08}{} - Present

\smallskip

\smallskip
\textbf{Economics Dept. Social Media Committee}
\par
Appointed Member
\hfill
Spring 2019 - Spring 2021

\smallskip

\textbf{Emory College Honors Program Standing Committee}
\par
Elected Member
\hfill
Fall 2019 - Spring 2021, Ran for reelection Spring 2021

\smallskip

\textbf{Emory College Faculty Senate}
\par
Senator (elected)
\hfill
\DatestampYMD{2025}{8}{} - \DatestampYMD{2028}{5}{}

\smallskip

\textbf{Emory University School of Law - Center for Law and Social Sciences}
\par
Invited Board Member
\hfill
Spring 2020 - Present

%%%%%%%%%%%%%%%%%%%%%%%%%%
% SEMINAR & CONFERENCE PRESENTATIONS  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%


\section
{Seminars and conferences}
{Seminars}
{PDF:Seminars}
\par
2026: Yale University, APSA, ACPE. 2025: University of Notre Dame. 2022: WFP, JDC. 2021: BREAD, UNHCR, PacDev, University of Georgia. 2020: JDC. 2019: Brigham Young University, UGA, William \& Mary, Georgia Tech ``Challenges in Development'', Western Economics Association. 2018: Emory University. 2017: APPAM; SEA; NEUDC; The World Bank; EPED; Secretaria Especial do Assuntos Estrat\'{e}gicos, Presid\^{e}ncia da Rep\'{u}blica (Brasil); Minist\'{e}rio da Ind\'{u}stria, Com\'{e}rcio Exterior e Servi\c{c}os (Brasil). 2016: Oklahoma State University, Univ. Javeriana Bogot\'{a}, IFPRI, Banco de la Republica (Colombia), NEUDC, Trinity University. 2015: Univ. of California, Riverside, IZA/World Bank Conference on Employment and Development, Univ. of Cologne, The World Bank, DEVPEC, Cornell Dyson GSA, APPAM. 2014 and previous: NEUDC, Universidad de los Andes, NYSEA 2012, MEA 2012.

%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROFESSIONAL REVIEW ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section
{Professional Service}
{Review}
{PDF:Review}
\par Referee: American Economic Review, Review of Economic Studies, Econometrica, Journal of Political Economy, Review of Economics and Statistics, Economic Journal, American Journal of Political Science, American Political Science Review, American Economic Journal: Economic Policy, European Economic Review, Journal of Development Economics, World Development, World Bank Economic Review, Journal of Public Economics, Economics of Education Review, Journal of Development Effectiveness, Journal of Environmental Economics and Management, Management Science, Economic Development and Cultural Change, Econometric Reviews, Feminist Economics, PNAS Nexus, Journal of Regional Science, Journal of Economic Geography*, Regional Studies, Journal of Comparative Economics, Journal of Economic Education, Spatial Economic Analysis. Other review: 3ie grant review, NSF SBS (Economics) Grant Review, World Bank KCP Program Grant Review, World Bank Development Impact/i2i Grant Program, DFID-IZA Growth in Labor Markets Research Grant Program, Oxford University Press.

%%%%%%%%%%%%%%%%%%%%%%%%%%
% GRANTS & AWARDS AND HONORS  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section
{Grants\newline
\& Awards}
{Competitive Grants \& Awards}
{PDF:GrantsAwards}
\par
\BulletItem
JPAL/IPA Displaced Livelihoods Initiative, \$227,885 for "\textit{From Displacement to Resilience: Aid, Economic Recovery, and Social Cohesion in Post-War Iraq}'' (co-PI with Andrea Caflisch, Daniel Masterson, and Julia Smith-Omomo.) 
 
\BulletItem
United Nations High Commissioner for Refugees, 2018-2023: \$693,655, for ``\textit{Design and Evaluation of Targeted Humanitarian Cash Transfers}'' (Co-PI with Onur Altındağ.)

\BulletItem
Russell Sage Foundation, 2021-2022: \$34,222, for ``\textit{Leadership Structure, Group Gender Composition, and Women’s Influence in Groups: A Field Experiment}''
\BulletItem
Emory University Research Committee (URC) Halle Institute for Global Research Award, 2021-2022: \$28,824, for ``\textit{Ethnic Diversity, Economic Integration of Refugees, and Firm Behavior: Insights from a field study in Southeastern Turkey}''
\BulletItem
Emory PERS Grant, 2019-2020: \$8,500
\BulletItem
The World Bank/ComPEL, \$25,000. Co-PI with Andreas Menzel (CERGE-EI). April 2017.
\BulletItem
National Science Foundation Graduate Research Fellowship Program--2012 Honorable Mention
\BulletItem
World Bank 2012 Finance and Private Sector Development (FPD) Academy Award: ``Local Industrial Structures and Female Entrepreneurship in India''
\BulletItem
Chancellor's Fellowship, City University of New York, 2010-2015.

%%%%%%%%%%%%%%%%%%%%%%%%%%
% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}


\textbf{The World Bank},
Washington, DC, USA
\par
Lead Specialist/Principal Investigator (occasional)
\hfill
\DatestampYMD{2016}{05}{} -- 
\DatestampYMD{2018}{06}{}

\smallskip


\par
Consultant (occasional)
\hfill
\DatestampYMD{2010}{01}{} -- 
\DatestampYMD{2016}{05}{}

\smallskip

\textbf{Compass-Lexecon},
Washington, DC, USA
\par
Analyst
\hfill
\DatestampYMD{2007}{06}{} --
\DatestampYMD{2010}{01}{}


%%%%%%%%%%%%%%
% LANGUAGES %%
%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English: native; Spanish: conversational (speaking, reading, writing).

%\newpage 
%
%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\end{body}

\label{LastPage}~
\end{document}